Towards Artificial Intelligence for Metaphysics: \\ the Case of the Inconsistency in G\"odel's Ontological Argument

### 2016-01-08 Papers/InProgress/IJCAI/paper.tex
Improve paragraphs about better performance with improved embedding

With the improved embedding for \SFiveU, the main theorem T3 can be derived from Scott's version of the axioms fully automatically. The
intermediate argumentation steps as not needed anymore to support the
prover.  This is shown in Fig.~\ref{ScottS5}. There it is also shown that the modal collapse can now be verified in
Isabelle/HOL with Meson. In previous work, with a less efficient embedding for \SFive, this failed.
\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/ScottS5.png}}
\caption{Full Automation of T3 and MC in \SFiveU } \label{ScottS5}
\end{figure}
\marginpar{ToDo: this picture has to be replaced by one without Isabelle errors}

>>>>

With the improved embedding for \SFiveU, the final theorem T3 (\textit{``Necessarily, there
exists God''}) can be derived from Scott's version of the axioms fully automatically. 
The fully automatic proof has been generated by the theorem prover \textsc{Leo-II}~\cite{C26} 
and subsequently verified in the proof assistant Isabelle/HOL~\cite{NPW02}, as shown in Fig.~\ref{ScottS5}. 
On the other hand, with the embedding used in \shortcite{C40}, 
the provers had to be given the intermediate theorem T2 and the corollary C in order to manage to prove T3.

Another evidence that the new embedding provides a significant performance boost 
is the successful automatic verification in Isabelle/HOL (with its automatic tactic Meson) of the modal
collapse \cite{Sobel}, which is one of the most strongly criticized
`side-effects' of G\"odel's and Scott's variants of the proof. In previous work \shortcite{C40}
the modal collapse has been proven by the higher-order provers
\textsc{Satallax} \cite{Satallax} and \textsc{Leo-II}, but a fully automatic
verification in the highly trusted Isabelle/HOL still failed \cite{ArchiveFormalProofsGoedelGod}. The success with the new embedding can be seen in Fig.~\ref{ScottS5}.

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{./Images/ScottS5.png}}
\caption{Full Automation of T3 and MC in \SFiveU } \label{ScottS5}
\end{figure}
\marginpar{ToDo: this picture has to be replaced by one without Isabelle errors}
